Loss recovery and tail loss performance in Multipath TCP

### 2016-12-04 main.tex
Fig Changes

\subsection{Testing with Deterministic loss patterns}
In order to understand the retransmission behavior of the Linux MPTCP implementation and to reproduce the observed retransmissions, we use a deterministic drop pattern.
Losses generated by using associating netem with corresponding interfaces and dropping the packets. This process is simplified by using the KAUNetem tool~\cite{Garcia2016}. 
MPTCP connection starts with a single TCP subflow and subsequently, one or more subflows are added following an agreement between client and server on the MPTCP protocol 
support and interface availability. So one has to wait in time and packets for the second subflow establishment to understand the MPTCP retransmissions. We send two bursts of 80 
packets each and drop tail packets on one of the interface. This is to ensure that the necessary and sufficient conditions for probe triggering are met and tail loss probe is generated on that
subflow. Three test cases are evaluated with one packet tail loss, two packet tail loss and  one packet along with probe loss. The expected retransmission behavior is shown in~\ref{timing}.

In Linux, TCP retransmission features are controlled by a sysctl setting tcp.early.retrans. It has 5 possible values with ranging from 0 to 4 with 3 being Linux default, enables both
ER and TLP. For this analysis, we used 0,3 and 4. In each setting, we calculate burst completion time for two burst of 80 packets each. The setup has server and client with MPTCP
enabled linux running on them. Client has two wireless interfaces with one way delay on each interface ranging from 20ms to 120ms. We consider 5 scenarios with delay pairings 20ms-20ms
20ms-30ms, 20ms-120ms, 30ms-20ms, 120ms-20ms to understand the effect of delay difference in the performance.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=610, natheight=400]{images/timing.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios}\label{timing}
\end{figure}

@@

Figure~\ref{1p} provides burst completion time comparison of different ER sysctl settings considered with one packet loss. The results show the improvements
in burst completion time with ER and TLP enabled compared to both disabled only when there is delay difference. The retransmission of lost packet follows the behavior 
depicted in Figure~\ref{timing}.

>>>>

\subsection{Testing with Deterministic loss patterns}
In order to understand the retransmission behavior of the Linux MPTCP implementation and to reproduce the observed retransmissions, we use a deterministic drop pattern.
Losses generated by using associating netem with corresponding interfaces and dropping the packets. This process is simplified by using the KAUNetem tool~\cite{Garcia2016}. 
MPTCP connection starts with a single TCP subflow and subsequently, one or more subflows are added following an agreement between client and server on the MPTCP protocol 
support and interface availability. So one has to wait in time and packets for the second subflow establishment to understand the MPTCP retransmissions. We send two bursts of 80 
packets each and drop tail packets on one of the interface. This is to ensure that the necessary and sufficient conditions for probe triggering are met and tail loss probe is generated on that
subflow. Three test cases are evaluated with one packet tail loss, two packet tail loss and  one packet along with probe loss.

In Linux, TCP retransmission features are controlled by a sysctl setting tcp.early.retrans. It has 5 possible values with ranging from 0 to 4 with 3 being Linux default, enables both
ER and TLP. For this analysis, we used 0,3 and 4. In each setting, we calculate burst completion time for two burst of 80 packets each. The setup has server and client with MPTCP
enabled linux running on them. Client has two wireless interfaces with one way delay on each interface ranging from 20ms to 120ms. We consider 5 scenarios with delay pairings 20ms-20ms
20ms-30ms, 20ms-120ms, 30ms-20ms, 120ms-20ms to understand the effect of delay difference in the performance. The expected retransmission behavior for different settings of ER is shown 
in~\ref{timingER0},~/\ref{timingER3} and ~\ref{timingER4}.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=610, natheight=400]{images/timingER0.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=0}\label{timingER0}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=610, natheight=400]{images/timingER3.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=3}\label{timingER3}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=610, natheight=400]{images/timingER4.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=4}\label{timingER4}
\end{figure}

@@

Figure~\ref{1p} provides burst completion time comparison of different ER sysctl settings considered with one packet loss. The results show the improvements
in burst completion time with ER and TLP enabled compared to both disabled only when there is delay difference. The retransmission of lost packet follows the behavior 
depicted in Figures~\ref{timingER0,timintER3,timingER4}.
